---
title: "Regression Project"
author: "Pat Ballard, Brent Lodge, Sean Morey"
date: "Spring 2018"
output: html_document
---

```{r setup, include=FALSE}
# Do not modify this chunk!
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(GGally)
library(scales)
library(readr)
library(Hmisc)
library(purrr)
library(tidyr)
library(gclus)
library(corrplot)
library(PerformanceAnalytics)
library(psych)
```

### Part 1: Importing and Examining Data
&nbsp;

#### 1.1 Importing Data

```{r 1.1}
pairs.panels(comm_prop, scale=TRUE, ci =T, stars = T)
```
#### 1.2 Examining Variable Distribution

```{r 1.1}
pairs.panels(comm_prop, scale=TRUE, ci =T, stars = T)
```
This plot gives a number of different observations; RentRate *appears* to be a relatively normal distribution, while all others appear skewed in some way. Age has a gap between 5 and 10 years, possibly indicating some sort of recession where building came to a halt. SqFt and Taxes are skewed identically to the right. While W2MiDT is not a continuous variable, there are more buildings in this sample outside of 2 miles than within, posibbly indicating some sort of urban sprawl in this city.

&nbsp;

#### 1.2 Add to existing data frame

```{r 1.2, results='asis'}
temp.diff.df <- [Enter your code here]
# Do not modify the following code:
knitr::kable(temp.diff.df, format = "markdown")
```
